Development Of Parallel Matrix Operations

### 2011-02-14 paper/paper.tex
Add all images and data tables

\begin{center}
\begin{tabular}{|r|r|r|r|r|r|r|}\hline
{\em n} & {\em K} & {\em T (msec)} & {\em Speedup} & {\em Eff} & {\em EDSF} \\\hline
1000    & seq     & 0000000        &   xxx         & xxx       & xxx        \\\hline
1000    & 1       & 0000000        & 0.0000        & 0.0000    & xxx        \\\hline
1000    & 2       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
1000    & 4       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
1000    & 8       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
1000    & 16      & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & seq     & 0000000        &   xxx         & xxx       & xxx        \\\hline
500     & 1       & 0000000        & 0.0000        & 0.0000    & xxx        \\\hline
500     & 2       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & 4       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & 8       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & 16      & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & seq     & 0000000        &   xxx         & xxx       & xxx        \\\hline
100     & 1       & 0000000        & 0.0000        & 0.0000    & xxx        \\\hline
100     & 2       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & 4       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & 8       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & 16      & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|r|r|r|r|r|r|r|}\hline
{\em n} & {\em K} & {\em T (msec)} & {\em Speedup} & {\em Eff} & {\em EDSF} \\\hline
1000    & seq     & 0000000        &   xxx         & xxx       & xxx        \\\hline
1000    & 1       & 0000000        & 0.0000        & 0.0000    & xxx        \\\hline
1000    & 2       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
1000    & 4       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
1000    & 8       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
1000    & 16      & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & seq     & 0000000        &   xxx         & xxx       & xxx        \\\hline
500     & 1       & 0000000        & 0.0000        & 0.0000    & xxx        \\\hline
500     & 2       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & 4       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & 8       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & 16      & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & seq     & 0000000        &   xxx         & xxx       & xxx        \\\hline
100     & 1       & 0000000        & 0.0000        & 0.0000    & xxx        \\\hline
100     & 2       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & 4       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & 8       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & 16      & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|r|r|r|r|r|r|r|}\hline
{\em n} & {\em K} & {\em T (msec)} & {\em Speedup} & {\em Eff} & {\em EDSF} \\\hline
1000    & seq     & 0000000        &   xxx         & xxx       & xxx        \\\hline
1000    & 1       & 0000000        & 0.0000        & 0.0000    & xxx        \\\hline
1000    & 2       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
1000    & 4       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
1000    & 8       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
1000    & 16      & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & seq     & 0000000        &   xxx         & xxx       & xxx        \\\hline
500     & 1       & 0000000        & 0.0000        & 0.0000    & xxx        \\\hline
500     & 2       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & 4       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & 8       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
500     & 16      & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & seq     & 0000000        &   xxx         & xxx       & xxx        \\\hline
100     & 1       & 0000000        & 0.0000        & 0.0000    & xxx        \\\hline
100     & 2       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & 4       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & 8       & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
100     & 16      & 0000000        & 0.0000        & 0.0000    & 0.0000     \\\hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{|r|r|r|r|r|r|r|}\hline
{\em n} & {\em K} & {\em T (msec)} & {\em Speedup} & {\em Eff} & {\em EDSF} \\\hline
1000    & seq     &  22        & xxxxx       & xxxxx   & xxxxx     \\\hline
1000    & 1       &  47        & 0.468       & 0.468   & xxxxx     \\\hline
1000    & 2       &  40        & 0.550       & 0.275   & 0.702     \\\hline
1000    & 4       &  34        & 0.647       & 0.162   & 0.631     \\\hline
1000    & 8       &  35        & 0.629       & 0.079   & 0.708     \\\hline
2000    & seq     &  83        & xxxxx       & xxxxx   & xxxxx     \\\hline
2000    & 1       &  90        & 0.922       & 0.922   & xxxxx    \\\hline
2000    & 2       &  35        & 2.371       & 1.186   & -0.222    \\\hline
2000    & 4       &  14        & 5.929       & 1.482   & -0.126    \\\hline
2000    & 8       &   9        & 9.222       & 1.153   & -0.029    \\\hline
4000    & seq     &  338       & xxxxx       & xxxxx   & xxxxx     \\\hline
4000    & 1       &  340       & 0.994       & 0.994   & xxxxx     \\\hline
4000    & 2       &  177       & 1.910       & 0.955   & 0.041     \\\hline
4000    & 4       &  91        & 3.714       & 0.929   & 0.024     \\\hline
4000    & 8       &  34        & 9.941       & 1.243   & -0.029    \\\hline
\end{tabular}
\end{center}

@@

Sequential and Parallel Implementation
\begin{center}
\begin{tabular}{|r|r|r|r|r|r|r|}\hline
{\em n} & {\em K} & {\em T (msec)} & {\em Speedup} & {\em Eff} & {\em EDSF} \\\hline
1000    & seq     &   32609        &   xxx         & xxx       & xxx        \\\hline
1000    & 1       &   53546        & 0.609        & 0.609    & xxx        \\\hline
1000    & 2       &   15812        & 2.062        & 1.031    & -0.409     \\\hline
1000    & 4       &    8101        & 4.025        & 1.006    & -0.132     \\\hline
1000    & 8       &    4703        & 6.934        & 0.991    & -0.064     \\\hline
1000    & 8       &    4210        & 7.746        & 0.968    & -0.053     \\\hline
500     & seq     &    4797        &   xxx         & xxx       & xxx        \\\hline
500     & 1       &    2046        & 2.345         & 2.345     & xxx        \\\hline
500     & 2       &    2632        & 1.823         & 0.911      & 1.573      \\\hline
500     & 4       &    1411        & 3.400         & 0.850     & 0.586      \\\hline
500     & 7       &     953        & 5.034         & 0.719     & 0.377      \\\hline
500     & 8       &     789        & 6.080         & 0.760     & 0.298      \\\hline
100     & seq     &      71        &   xxx         & xxx       & xxx        \\\hline
100     & 1       &      62        & 1.145        & 1.145    & xxx        \\\hline
100     & 2       &      42        & 1.690        & 0.845    & 0.355     \\\hline
100     & 4       &      36        & 1.972        & 0.493    & 0.441     \\\hline
100     & 7       &      35        & 2.029        & 0.290    & 0.492     \\\hline
100     & 8       &      35        & 2.029        & 0.254    & 0.502     \\\hline
\end{tabular}
\end{center}

Sequential Strassen and Parallel Strassen Implementation
\begin{center}
\begin{tabular}{|r|r|r|r|r|r|r|}\hline
{\em n} & {\em K} & {\em T (msec)} & {\em Speedup} & {\em Eff} & {\em EDSF} \\\hline
1000    & seq     &   12296           &   xxx         & xxx       & xxx        \\\hline
1000    & 1       &   12105           &   1.016       & 1.016     & xxx        \\\hline
1000    & 2       &   7139            &   1.722       & 0.861     & 0.180      \\\hline
1000    & 4       &   4184            &   2.939       & 0.735     & 0.128      \\\hline
1000    & 8       &   2467            &   4.984       & 0.712     & 0.071      \\\hline
1000    & 8       &   2372            &   5.184       & 0.648     & 0.081      \\\hline
500     & seq     &   1792            &   xxx         & xxx       & xxx        \\\hline
500     & 1       &   1787            &   1.003       & 1.003     & xxx        \\\hline
500     & 2       &   1112            &   1.612       & 0.806     & 0.245      \\\hline
500     & 4       &   713             &   2.513       & 0.628     & 0.199      \\\hline
500     & 7       &   505             &   3.549       & 0.507     & 0.163      \\\hline
500     & 8       &   502             &   3.570       & 0.446     & 0.178      \\\hline
100     & seq     &   71              &   xxx         & xxx       & xxx        \\\hline
100     & 1       &   37              &   1.919       & 1.919     & xxx        \\\hline
100     & 2       &   69              &   1.029       & 0.514     & 2.730      \\\hline
100     & 4       &   70              &   1.014       & 0.254     & 2.189      \\\hline
100     & 7       &   68              &   1.044       & 0.149     & 1.977      \\\hline
100     & 8       &   68              &   1.044       & 0.131     & 1.958      \\\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|r|r|r|r|r|r|r|}\hline
{\em n} & {\em K} & {\em T (msec)} & {\em Speedup} & {\em Eff} & {\em EDSF} \\\hline
1000    & seq     &  5374          & xxxxx        & xxxxx    & xxxxx     \\\hline
1000    & 1       &  4412          & 1.218        & 1.218    & xxxxx     \\\hline
1000    & 2       &  2393          & 2.246        & 1.123    & 0.085     \\\hline
1000    & 4       &  1392          & 3.861        & 0.965    & 0.087     \\\hline
1000    & 7       &  960           & 5.598        & 0.800    & 0.087     \\\hline
1000    & 8       &  1851          & 2.903        & 0.363    & 0.337     \\\hline
500     & seq     &  475           & xxxxx        & xxxxx    & xxxxx     \\\hline
500     & 1       &  597           & 0.796        & 0.796    & xxxxx     \\\hline
500     & 2       &  372           & 1.277        & 0.638    & 0.246     \\\hline
500     & 4       &  249           & 1.908        & 0.477    & 0.223     \\\hline
500     & 7       &  222           & 2.140        & 0.306    & 0.267     \\\hline
500     & 8       &  324           & 1.466        & 0.183    & 0.477     \\\hline
100     & seq     &  17            & xxxxx        & xxxxx    & xxxxx     \\\hline
100     & 1       &  57            & 0.298        & 0.298    & xxxxx     \\\hline
100     & 2       &  64            & 0.266        & 0.133    & 1.246     \\\hline
100     & 4       &  66            & 0.258        & 0.064    & 1.211     \\\hline
100     & 7       &  80            & 0.212        & 0.030    & 1.471     \\\hline
100     & 8       &  101           & 0.168        & 0.021    & 1.882     \\\hline
\end{tabular}
\end{center}
